Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-09 paper2_JNLS/paper.tex
NM

\title{Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory}

% ORIGINAL: The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes
% Words: triggered, induced, generated, sparked

@@

A few comments are in order. First, we note that the original formulation of this theory utilized a slightly different normalization \cite{majda2019}, with identical powers of $\drat$ in \eqref{dimlessKdV} but with different expressions for the other dimensionless parameters. These differences are purely cosmetic, and we have made the choices above simply to facilitate comparison against the experiments. Second, an alternate formulation of the variable-depth KdV equation exists in which it is conjectured that the product $\depth^{1/4} \eta$, rather than $\eta$, varies continuously across the ADC \cite{johnson1997modern}. Of course, that assumption implies a discontinuity in surface displacement, which, though small, is physically unrealistic. We have chosen to enforce continuity of surface displacement in the above on the basis of physical realism. Using the alternative formulation would simply modify the power of $\drat$ in the second term of \eqref{dimlessKdV} by 1/4, i.e.~$\drat^{-7/4}$ instead of $\drat^{-3/2}$. Hence, all of the results discussed below would hold qualitatively in this alternate formulation, with only slight quantitative modifications.

>>>>

\title{Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory}

%experimental measurements and deterministic-statistical truncated KdV theory
% ORIGINAL: The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes
% Words: triggered, induced, generated, sparked

@@

A few comments are in order. First, we note that the original formulation of this theory utilized a slightly different normalization \cite{majda2019}, with identical powers of $\drat$ in \eqref{dimlessKdV} but with different expressions for the other dimensionless parameters. These differences are purely cosmetic, and we have made the choices above simply to facilitate comparison with experiments. Second, an alternate formulation of the variable-depth KdV equation has been proposed in which the product $\depth^{1/4} \eta$, rather than $\eta$, is conjectured to vary continuously across the ADC \cite{johnson1997modern}. Of course, that assumption implies a discontinuity in surface displacement, which, though perhaps small, would be physically unrealistic. We have chosen to enforce continuity of surface displacement on the basis of physical realism. Furthermore, our {\em direct experimental measurements} of $\etastd$ give no indication of a significant change across the ADC, thus supporting the formulation used here. We note, however, that the only modification resulting from the alternate formulation would be in the power of $\drat$ in the second term of \eqref{dimlessKdV}: the power $\drat^{-3/2}$ would become $\drat^{-7/4}$. Thus, in this alternate formulation, the second term in \eqref{dimlessKdV} would be scaled by a negative power of $\drat$ and the third term by exactly the same positive power of $\drat$. Hence, the two formulations are qualitatively very similar with only slight quantitative differences expected.
